Descriptive_Stats

### 2023-05-21 Code/RankComparison.Rmd
Changed variable names

#nine is used for 2019 and two is used for 2022.  H, S, F are used to denote the heats, semifinals, and finals.
colnames(inter) <- c("Athlete", "Country", "nineH", "nineS", "nineF", "twoH", "twoS", "twoF")
```

@@

# Define the grouping of bars
groupings <- list(c("nineH", "twoH"), c("nineS", "twoS"), c("nineF", "twoF"))

@@

# Create the bar graph
ggplot(means_df, aes(x = variable, y = mean, fill = variable)) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_fill_manual(values = c("sienna2", "tan", "sienna2", "tan", "sienna2", "tan")) +
  labs(x = "Variable", y = "Mean", title = "Grouped Bar Graph") +
  theme_minimal() +
  theme(legend.position = "none")
```

>>>>

#nine is used for 2019 and two is used for 2022.  H, S, F are used to denote the heats, semifinals, and finals.
colnames(inter) <- c("Athlete", "Country", "2019H", "2019S", "2019F", "2022H", "2022S", "2022F")
```

@@

# Define the grouping of bars
groupings <- list(c("2019H", "2022H"), c("2019S", "2022S"), c("2019F", "2022F"))

@@

# Create the bar graph
ggplot(means_df, aes(x = variable, y = mean, fill = variable)) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_fill_manual(values = c("sienna2", "tan", "sienna2", "tan", "sienna2", "tan")) +
  labs(y = "Mean Reaction Time", x ="") +
  theme_minimal() +
  theme(legend.position = "none")
ggsave(filename="2019vs2022BarGraph.pdf", path = "../Manuscript", height=4, width=6)
```
